Another DSL primer

### 2014-10-02 docs/fsml/paper.tex
Slightly updated FSML spec paper

0.00003 as of 25 December 2013.

@@

\begin{figure}[t!]
\vspace{-77\in}
\includegraphics[width=\textwidth]{../../languages/fsml/sample.pdf}
\vspace{-150\in}
\caption{A finite state machine for turnstiles.}
\label{F:turnstile}
\end{figure}

@@

\codefigure{%
The FSM of \autoref{F:turnstile} in the abstract syntax of the DGL language}{%
languages/fsml/sample.dgl}{%
prolog}

@@

\codefigure{%
The FSM of \autoref{F:turnstile} in the dot language}{%
languages/fsml/sample.dot}{%
dot}

The DGL processor translates the graph into a specification according
to the \emph{dot} language of
\emph{GraphViz}\footnote{\url{http://www.graphviz.org/}}; see
\autoref{languages/fsml/sample.dot}. The GraphViz tool
directly renders the dot specification as shown \autoref{F:turnstile}.

>>>>

0.00004 as of 2 October 2014.

@@

\begin{figure}[t!]
\vspace{-77\in}
\includegraphics[width=\textwidth]{../../languages/fsml/dot/sample.pdf}
\vspace{-150\in}
\caption{A finite state machine for turnstiles.}
\label{F:turnstile}
\end{figure}

@@

\codefigure{%
The FSM of \autoref{F:turnstile} in the abstract syntax of the DGL language}{%
languages/fsml/dot/sample.term}{%
prolog}

@@

\codefigure{%
The FSM of \autoref{F:turnstile} in the dot language}{%
languages/fsml/dot/sample.dgl}{%
dot}

The DGL processor translates the graph into the concrete syntax
of the \emph{dot} language of
\emph{GraphViz}\footnote{\url{http://www.graphviz.org/}}; see
\autoref{languages/fsml/sample.dot}. (That is, DGL can be viewed as a 
subset of the DOT language.) The GraphViz tool
directly renders the dot specification as shown \autoref{F:turnstile}.
